---
title: "ESM 244: Advanced Data Analysis HW#1"
author: "Nathaniel Burola"
date: "2/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW1: Data Wrangling and Visualization with Snowshoe Hares 

Installing all the relevant packages for this assignment 
```{r, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}
r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org"
options(repos = r)
install.packages("here")
install.packages("janitor")
install.packages("kableExtra")
install.packages("naniar")
install.packages("VIM")
install.packages("skimr")
install.packages("ggfortify")
install.packages("sf")
install.packages("tmap")
install.packages("tidyverse") 
install.packages("lubridate")
```

### Attaching all of the relevant packages for this assignment with the library 
```{r, echo = TRUE, message = FALSE, warning = FALSE}
library(tidyverse)
library(janitor)
library(here)
library(kableExtra)
library(naniar)
library(VIM)
library(skimr)
library(ggfortify)
library(sf)
library(tmap)
library(ggplot2)
library(lubridate)
```

### Reading in the data to form a new dataframe 
```{r}
snowshoe <- read_csv(here("data", "showshoe_lter.csv"))
```

### Data exploring and wrangling 
```{r}
summary(snowshoe) #Gives a summary of how many different variables there are in the dataframe
View(snowshoe) #Opens a new dataframe with the dataset already in it 
names(snowshoe) #Gives the number of column headers in the data set 
head(snowshoe) #Gives a preview of the data set 
tail(snowshoe) #Gives a preview of the data set 

#Initial reaction: Columns that include NA data are the following: time, right ear, sex, age, hindfoot, and notes. 

#What variables may be related to each other with this data? Could include sex, age, and weight. Maybe grid and date? 

#What do you want to graph with the snowshoe data? 

#Statement: I want to see how the weight of all the snowshoe hares both female and male will vary across the years of the study 
```

#Filtering and constructing a new dataframe with desired variables 
```{r}
snowfiltered = subset(snowshoe, select = -c(time, grid, trap, l_ear, r_ear, hindft, notes, b_key, session_id, study)) #Filtered out all the columns that are not desired in the new dataframe 

#Transforming all of the classes of the variables from character to numeric 
as.numeric("weight")
as.numeric("sex")
as.numeric("age")
```

### Trying to filter the date column by year 
```{r}

snow <- strptime(as.Date(snowfiltered$date), "%m/%d/%y")

class(snowfiltered$date)
snow

mutate(snowfiltered, date_new = snow)


```



### Descriptive introductory summary of what the project is all about (3-4 sentences)  
```{r}

```

### Map of the study area with images of snowshoe hares
```{r}

```

### Finalized graph about the Bonanza Creek snowshoe hare population  
```{r}
snowgraph <- ggplot(snowfiltered, aes(date, weight)) + 
  geom_point()

snowgraph

```

